An efficient contact value approach to approximating the pair distribution function of the inhomogeneous hard-sphere fluid

### 2014-07-08 papers/pair-correlation/paper.tex
clean up text just a bit more Tested on bennet. Took 0:18.58.

We have performed a separable fit to the Monte-Carlo simulated radial
distribution function.  We chose to focus our fit on the range of
distances $r_{12} < 2\sigma$.  This range of distances is relevant to
the widely used \fixme{add citations?}  Statistical Associating Fluid
Theory of Variable Range (SAFT-VR) free energy with square-well
dispersive attraction developed by Gil-Villegas \emph{et
  al.}~\cite{gil1997statistical}.  For comparison, in
Fig.~\ref{fig:radial-distribution} we plot our fit, Monte-Carlo data,
and the radial distribution function of Gil-Villegas \emph{et al.},
which we have extracted from their approximation for the first term in
the dispersion free energy given by Eq.~\ref{eq:mean-field}.

For ease of implementation and future extension to larger radii, we
chose to express our fit with a polynomial function, multiplied by an
exponential decay.  We constrain our functional form for $g_S(r,
g_\sigma)$ to match the value at contact:
\begin{equation}
  g_S(\sigma, g_\sigma) = g_\sigma.
\end{equation}
Beyond this constraint we have:
\begin{align}
  g_S(r,g_\sigma) &=
  1 + \left(\sum_{i=1}^{4} \sum_{j=1}^{4} \kappa_{ij} h_\sigma^i
  \zeta^j\right)e^{-\alpha \zeta} \label{eq:fit-form}
\end{align}
where $h_\sigma = g_\sigma - 1$ is the total correlation function at
contact, and $\zeta \equiv \frac{r}{\sigma}-1$ is a dimensionless
measure of the distance from contact.

\begin{table}
  \begin{align*}
    \kappa &= \kappatable
  \end{align*}
  \caption{The fitted $\kappa_{ij}$ matrix.
    %% In addition to these 12 parameters, we also optimized the
    %% exponetial decay constant $\alpha=\alphaval$.za
    %% Note that the first column of $\kappa$ corresponds to $j=1$
    %% while the first row corresponds to $i=1$ in
    %% Eq.~\ref{eq:fit-form}.
  }
\end{table}

The Gil-Villegas function is fit to data for $r <= \maxrfit R$.  The
maximum error within this radius in $g_S(r)$ at packing fractions up
to 0.45 is \maxerr, which occurs at $\eta = \etamaxerr$ and $r =
\rmaxerr R$.  We used in this fit Monte Carlo data for the radial
distribution function at values of packing fraction at increments of
0.05 from 0.05 to 0.45. Fig.~\ref{fig:radial-distribution} displays
our approximation at just under half of the densities that were
included in the fit.

>>>>

We have performed a separable fit to the Monte-Carlo simulated radial
distribution function.  We chose to focus our fit on the range of
distances $r_{12} \le \maxrfit R$.  This range of distances is relevant to
the widely used \fixme{add citations?}  Statistical Associating Fluid
Theory of Variable Range (SAFT-VR) free energy with square-well
dispersive attraction developed by Gil-Villegas \emph{et
  al.}~\cite{gil1997statistical}.  For comparison, in
Fig.~\ref{fig:radial-distribution} we plot our fit, Monte-Carlo data,
and the radial distribution function of Gil-Villegas \emph{et al.},
which we have extracted from their approximation for the first term in
the dispersion free energy given by Eq.~\ref{eq:mean-field}.

\begin{table}
  \begin{align*}
    \kappa &= \kappatable
  \end{align*}
  \caption{The fitted $\kappa_{ij}$ matrix.
    %% In addition to these 12 parameters, we also optimized the
    %% exponetial decay constant $\alpha=\alphaval$.za
    %% Note that the first column of $\kappa$ corresponds to $j=1$
    %% while the first row corresponds to $i=1$ in
    %% Eq.~\ref{eq:fit-form}.
  }\label{tab:kappa}
\end{table}

For ease of implementation and future extension to larger radii, we
chose to express our fit with a fourth-order polynomial.  We constrain
our functional form for $g_S(r, g_\sigma)$ to match the value
$g_\sigma$ at contact and to reproduce $g(r)=1$ in the low-density
($g_\sigma =1$) limit.  Incorporating these constraints we have the
functional form:
\begin{align}
  g_S(r,g_\sigma) &=
  g_\sigma + \sum_{i=1}^{4} \sum_{j=1}^{4} \kappa_{ij} (g_\sigma - 1)^i
  \left(\tfrac{r}{\sigma}-1\right)^j.
  \label{eq:fit-form}
\end{align}
where the matrix $\kappa_{ij}$ is determined from our least-squares
fit to Monte Carlo data for the radial distribution function, over the
range $2R \le r \le \maxrfit R$, and for packing fractions $\eta \le
0.45$.  The resulting parameters are displayed in
Table~\ref{tab:kappa}.  The maximum error in $g_S(r)$ within this
range is \maxerr, which occurs at $\eta = \etamaxerr$ and $r =
\rmaxerr R$.  Fig.~\ref{fig:radial-distribution} displays
our approximation at just under half of the densities that were
included in the fit.
